MLH1 Data Report

### 2019-12-20 doc/Main_Report_Results.rmd
re-structing results file to match outline

#setwd("~./MLH1repo/doc/")
setwd("C:/Users/alpeterson7/Documents/MLH1repo/")
#setwd("C:/Users/April/Desktop/MLH1repo")
#load(file="data/MLH1/MLH1_data_setup.RData")

@@

load(file="~./data/MLH1/MLH1_data_setup_12.20.19.RData")#fixing bugs, formating
#load(file="data/MLH1/MLH1_data_setup_12.3.19.RData")#removed exclude mice
#load(file="data/MLH1/MLH1_data_setup_11.12.19.RData")#added batch17
#load(file="data/MLH1/MLH1_data_setup_11.11.19.RData")#deleted DUP image
#load(file="data/MLH1/MLH1_data_setup_9.26.19.RData")#added batch16
#load(file="data/MLH1/MLH1_data_setup_8.29.19.RData") #
#load(file="data/MetaData.RData") #this was replacing most updated data file

@@

write.table(AP_category_table, "~./MLH1repo/strain_table_variances.csv", sep=",", row.names = FALSE)

@@

# MLH1 means

@@

# Mixed Models

@@

For mouse averages of MLH1 counts, only strain with observations for both sexes and are from Mus species.

@@

# Variance in CO count

@@

```{r var.mod.3, echo=FALSE}

@@

# DMC1 Results

@@

@@

# Proportion of chrm classes

```{r chrm_prop_data, echo=FALSE}
chrm.class.DF = read.csv("~./MLH1repo/data/ChrmClassProportions.csv", header = TRUE)

melt.table = read.csv("~./MLH1repo/data/ChrmClassProportions_melt.csv", header = TRUE)
melt.table$fileName <- (melt.table$Original.Name)

```{r chrm.pro.Curated.BivData, echo=FALSE}

#bivalent data might be too big..
load(file="~./MLH1repo/data/CleanBivData.RData")
#Curates_BivData -- hand.foci.count!

>>>>

#setwd("~./MLH1repo/doc/")
setwd("C:/Users/alpeterson7/Documents/MLH1repo/doc/")
#setwd("C:/Users/April/Desktop/MLH1repo")
#load(file="data/MLH1/MLH1_data_setup.RData")

@@

load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_12.20.19.RData")#fixing bugs, formating
#load(file="data/MLH1/MLH1_data_setup_12.3.19.RData")#removed exclude mice
#load(file="data/MLH1/MLH1_data_setup_11.12.19.RData")#added batch17
#load(file="data/MLH1/MLH1_data_setup_11.11.19.RData")#deleted DUP image
#load(file="data/MLH1/MLH1_data_setup_9.26.19.RData")#added batch16
#load(file="data/MLH1/MLH1_data_setup_8.29.19.RData") #
#load(file="data/MetaData.RData") #this was replacing most updated data file

@@

#there might be an error for changing wd
#write.table(AP_category_table, "~./MLH1repo/strain_table_variances.csv", sep=",", row.names = FALSE)

@@

# Main Figures

@@

add code for the table table. may have to deal with the excess mouse issue

# A. Models for mean and variance of MLH1 foci per cell

@@

FOR FINAL ANALYSIS, MOL Will be coded as a seperate subsp (change all of the main model reports to)
For mouse averages of MLH1 counts, only strain with observations for both sexes and are from Mus species.

@@

## Variance in CO count

@@

```{r var.mod.3, echo=FALSE, eval=FALSE}

@@

# Rapid male specific evolution

## Proportion of chrm classes

```{r chrm_prop_data, echo=FALSE, eval=FALSE}
#shut off eval for now because of wd / path error
#chrm.class.DF = read.csv("~./MLH1repo/data/ChrmClassProportions.csv", header = TRUE)

#melt.table = read.csv("~./MLH1repo/data/ChrmClassProportions_melt.csv", header = TRUE)
melt.table$fileName <- (melt.table$Original.Name)

```{r chrm.pro.Curated.BivData, echo=FALSE, eval=FALSE}

#bivalent data might be too big..
#load(file="~./MLH1repo/data/CleanBivData.RData")
#Curates_BivData -- hand.foci.count!

## DMC1 Results

@@

## Total SC Results

# Female patterns

there is strain specific evolution for females ...

# Sexual dimorphism and heterochiasmy things

total sc length / SC compaction and telomere bias in positioning are conserved / consistantly sexually dimorphism (in these mice?)  for most species

# Predictions / tests for selection on Bivalent structure

# ""

@@
